---
Title: "Learning to reference figures, tables and sections"
Author: "Rachel Xinrui WANG"
Date: "`r Sys.Date()`"
output:
  bookdown::html_document2
keep_md: true
---

create branch: git checkout -b branchname
move between branches: git branch branchname
delete branch: git branch -d branchname

Steps to update:
git add .
git commit -m 'message'
git push / git push origin branchname


```{r global, include=FALSE}
knitr::opts_chunk$set(fig.align = "center")
```

```{r message=FALSE}
library(tidyverse)
```

# learning to reference figures {#figures}

```{r FigRef, fig.cap="This is a line plot."}
x = seq(1:100)
y = rnorm(100)
dat = data.frame(x, y)
ggplot(dat, aes(x = x, y = y)) +
geom_line()
```

In figure \@ref(fig:FigRef), we have plotted x versus y.

# Learning to reference tables {#tables}

In table \@ref(tab:TabRef), we have shown the first five rows of the data

```{r TabRef}
head(dat,5) %>% 
  knitr::kable(caption = "First five rows of the data")
```

# Learning to reference sections

in Section \@ref(figures) we plotted a figure, while in Section \@ref(tables) we produced a table